Single Bivalent Level Analysis

### 2020-01-22 doc/Bivalent_Analysis.Rmd
a few small notes from home

setwd("C:/Users/alpeterson7/Documents/MLH1repo/")
#setwd("C:/Users/April/Desktop/MLH1repo")
#load(file="data/MLH1/MLH1_data_setup.RData")

#load Clean BivData
load(file="data/CleanBivData_1.21.20.RData")

#load other data files, MLH1
load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.5.20.RData")#added batch18

@@

>>>>

#setwd("C:/Users/alpeterson7/Documents/MLH1repo/")
#setwd("C:/Users/April/Desktop/MLH1repo")
#load(file="data/MLH1/MLH1_data_setup.RData")

setwd("~./MLH1repo/")
#load Clean BivData
load(file="data/CleanBivData_1.21.20.RData")

#load other data files, MLH1
load(file="~./MLH1repo/data/MLH1_data_setup_1.5.20.RData")#added batch18

#load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.5.20.RData")#added batch18

@@

#chromosome Size effect

because of chromosome size effect on CO position and rate, I'd like to try seperate bins of the 'loss' bivalents
how does within cell variance in SC length compare across cells?

```{r chrm.size.effect, echo=FALSE}

show.the.cells_females <- ggplot(whole.cell.data_manual[whole.cell.data_manual$sex == "female",], aes(x=fileName, y= SC.length, color=strain))+geom_point()+ facet_wrap(~strain, scales="free")+ylim(c(30,200))+ggtitle("Female whole cell manual measures")
show.the.cells_females
#PWD seems to have the biggest variance across cells

#the min is pretty stable

show.the.cells_male <- ggplot(whole.cell.data_manual[whole.cell.data_manual$sex == "male",], aes(x=fileName, y= SC.length, color=strain))+geom_point()+ facet_wrap(~strain, scales="free")+ylim(c(30,150))+ggtitle("Male whole cell manual measures")
show.the.cells_male

#WSB has more min

#almost_whole_cell

#almost_whole_cell_BivData
almost_whole_cell_wsb <- almost_whole_cell_BivData[almost_whole_cell_BivData$strain == "WSB",]

almost_whole_cell_DOM <- almost_whole_cell_BivData[almost_whole_cell_BivData$subsp == "Dom",]
almost_whole_cell_MUSC <- almost_whole_cell_BivData[almost_whole_cell_BivData$subsp == "Musc",]

show.the.almost_cells_DOM_m <- ggplot(almost_whole_cell_DOM[almost_whole_cell_DOM$sex == "male",], aes(x=fileName, y= chromosomeLength, color=strain))+
  geom_point()+ facet_wrap(~strain, scales="free")+ylim(c(30,150))+ggtitle("Male whole cell BivData measures")

show.the.almost_cells_DOM_m
```

given the distributions of sc lengths within cells -- do I think I can predict a random SC's length (rank)
